Inference for Trans-dimensional Bayesian Models with Diffusive Nested Sampling

### 2014-12-07 Documents/Paper/ms.tex
Three new NS references

\subsection{Diffusive Nested Sampling}
The main difficulty with Nested Sampling is coming up with methods to sample
the constrained prior distributions of Equation~\ref{eq:constrained_prior}.
Diffusive Nested Sampling
\citep[DNS][]{dnest} is an alternative version of Nested Sampling that is
appropriate when MCMC is used to explore the parameter space.
A C++ implementation of DNS, called {\tt DNest3}, is available at
{https://github.com/eggplantbren/DNest3}.

@@

@@

>>>>

\subsection{Diffusive Nested Sampling}
The main difficulty with Nested Sampling is coming up with methods to sample
the constrained prior distributions of Equation~\ref{eq:constrained_prior}.
Various implementations of Nested Sampling exist, with different strategies
for sampling Equation~\ref{eq:constrained_prior}
\citep[e.g.][]{multinest, diamonds, radfriends}.

Diffusive Nested Sampling
\citep[DNS][]{dnest} is an alternative version of Nested Sampling that is
appropriate when MCMC is used to explore the parameter space.
A C++ implementation of DNS, called {\tt DNest3}, is available at
{https://github.com/eggplantbren/DNest3}.

@@

\bibitem[Buchner (2014)]{radfriends}
Buchner, Johannes.~A statistical test for Nested Sampling algorithms.~Statistics
and Computing (2014): 1-10.

\bibitem[Corsaro and De 
Ridder(2014)]{diamonds} Corsaro, E., De Ridder, J.\ 2014.\ DIAMONDS: A new Bayesian nested sampling tool. Application to peak bagging of solar-like oscillations.\ Astronomy and Astrophysics 571, AA71.

@@

\bibitem[\protect\citeauthoryear{Feroz, Hobson,
\& Bridges}{2009}]{multinest} Feroz F., Hobson M.~P., Bridges M., 2009, MNRAS, 398, 1601
